Research

### 2025-10-09 research.qmd
profile update

1. **Smartphone Use, Social Support, and Sleep Health.** Shaokang Yang, Idris Adjerid. [SSRN](http://dx.doi.org/10.2139/ssrn.5368531) — *Under Review at **Information Systems Research***  
   - Accepted to WISE, Nashville, TN, Dec 17–19, 2025  
   - Accepted to Conference on Health IT and Analytics (CHITA), Washington, DC, May 2024  
   - Presented to Doctoral Consortium of CHITA, Washington, DC, May 2024  
   - Presented to 33rd Annual POMS Conference, Orlando, FL, May 2023  
   - Accepted to CHITA, Washington, DC, May 2023

@@

-   Shaokang Yang, Idris Adjerid. *Friends over Feeds: How Social Smartphone Use Reduces Screen Time.* *Doctoral Consortium of CHITA*, Austin, TX, Apr 2025.

@@

>>>>

1. **Smartphone Use, Social Support, and Sleep Health.** Shaokang Yang, Idris Adjerid. [SSRN](http://dx.doi.org/10.2139/ssrn.5368531) — *Under Review at **Information Systems Research***  
   - Accepted to WISE, Nashville, TN, Dec 17–19, 2025  
   - Accepted to Conference on Health IT and Analytics (CHITA), Washington, DC, May 2024  
   - Presented at Doctoral Consortium of CHITA, Washington, DC, May 2024  
   - Presented at 33rd Annual POMS Conference, Orlando, FL, May 2023  
   - Accepted to CHITA, Washington, DC, May 2023

@@

@@

-   Shaokang Yang, Idris Adjerid. *Friends over Feeds: How Social Smartphone Use Reduces Screen Time.* *Doctoral Consortium of CHITA*, Washington, DC, May 2024.
